\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-07-27 sections/results.tex
Figures are now confined to their own sections
Update caption for 'otu_correlations' and 'network_comparison' figures

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=15.8cm]{otu_corr_full.pdf}
      \caption{\textbf{Correlation between the abundances of taxa in OTU tables generated using various clustering and denoising methods}. }
      \label{fig:otu_correlations}
    \end{center}
  \end{figure}

@@

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=17.8cm]{net_inference_comparison.pdf}
      \caption{\textbf{Variance of the co-occurrence networks for different processing pipelines}.  Node (\textbf{a})  and edge (\textbf{b}) overlap between all different networks generated from the data.}
      \label{fig:network_heatmap}
    \end{center}
  \end{figure}

>>>>

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=15.8cm]{otu_corr_full.pdf}
      \caption{
        \textbf{Comparison of various denoising and clustering algorithms used in the pipeline}.
        (A, B) Correlation of the abundances of the taxa that are common between the count matrices created by two different methods.
        (A) The best correlation (most similar methods) is between open-reference and denovo.
        (B) The worst correlation (least similar methods) is between open-reference and dada2.
        (C) A heatmap showing the $\mathrm{R}^2$ of all pairwise comparisons of the methods.
      }
      \label{fig:otu_correlations}
    \end{center}
  \end{figure}

@@

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=17.8cm]{net_inference_comparison.pdf}
      \caption{
        \textbf{Networks generated using different network inference methods}.
        The four different networks generated by different network inference methods are very dissimilar (C).
        (A) The overlaps between the edges among the network5 generated is shown. The number of edges that are common to all networks are very low (5).
        (B) The hamming distance between the networks is shown. The similarity between various methods was found to vary with the data-source used.
      }
      \label{fig:network_comparison}
    \end{center}
  \end{figure}
